Reading source files and preparing data sets

### 2024-11-17 data-raw/01-preprocessing-source-files.Rmd
Revisions to package configuration and reproducibility
Improved the documentation and fixed an issue with the Cycle 2 (1986) episode weights, which did not correctly use the number of decimals indicated in the user's guide

@@

```{r}
cycling_2015 <- cycling_2015 |>
  dplyr::select(PUMFID:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2015,
         MODE = "Cycling") |>
  dplyr::rename(ACTCODE = TUI_01)
```
Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2015 <- gss_m_2015[,c('PUMFID','LUC_RST','PRV')]

cycling_2015 <- cycling_2015 |> 
  left_join(gss_m_2015, by = 'PUMFID') |>  # Merging the two tables
  filter(LUC_RST %in% c(1,2,3)) |> 
  mutate(Pop_centre =
           case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "non CMA/CA"),
         Province = 
           case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia"))
```
Now, let's evaluate the count of episodes between each combination of
origin and destination:

@@

```{r}
usethis::use_data(cycling_2015, overwrite = TRUE)
```

@@

```{r}
rm(gss_e_2015,gss_m_2015)
```
## GSS 2010

@@

```{r}
walking_2010 <- walking_2010 |>
  dplyr::select(RECID, WGHT_EPI,ACTCODE, STARTIME:dest_label) |>
  mutate(YEAR = 2010,
         MODE = "Walking")
walking_2010 <- walking_2010 %>% dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE)
```
Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2010 <- gss_m_2010[,c('RECID','LUC_RST','PRV')]

@@

@@

```{r}
cycling_2010 <- cycling_2010 |>
  dplyr::select(RECID, WGHT_EPI,ACTCODE:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2010,
         MODE = "Cycling")
cycling_2010 <- cycling_2010 %>% dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE)
```
Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2010 <- gss_m_2010[,c('RECID','LUC_RST','PRV')]

cycling_2010 <- cycling_2010 |> 
  left_join(gss_m_2010, by = c( 'PUMFID' = 'RECID')) |>  # Merging the two tables
  filter(LUC_RST %in% c(1,2,3)) |> 
  mutate(Pop_centre =
           case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "non CMA/CA"),
         Province = 
           case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia"))
```
Now, let's evaluate the count of episodes between each combination of
origin and destination:

@@

```{r}
usethis::use_data(cycling_2010, overwrite = TRUE)
```
As we have already processed this year's data, we will clear the Episode and Main files for this year from the computer's memory before uploading any more data

```{r}
rm(gss_e_2010,gss_m_2010)
```
## GSS 2005

@@

```{r}
usethis::use_data(walking_2005, overwrite = TRUE)
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  dplyr::select(RECID, WGHT_EPI, ACTCODE:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2005,
         MODE = "Cycling")
cycling_2005 <- cycling_2005 |> dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE) 
```
Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2005 <- gss_m_2005[,c('RECID','LUC_RST','PRV')]

@@

```{r}
usethis::use_data(cycling_2005, overwrite = TRUE)
```
As we have already processed this year's data, we will clear the Episode and Main files for this year from the computer's memory before uploading any more data

```{r}
rm(gss_e_2005,gss_m_2005)
```
## GSS 1998

@@

The person was at home doing food cleanup (`ACTCODE` = 110), then
went for walking that lasted 30 minutes, came back home and spent 15 minutes relaxing/resting. Here have here another cas of a recreational/leisure trip!

@@

>>>>

Label the activity ("7" is "Transport to or from activity") and drop the LOCATION because it is already coded as MODE:    
```{r}
walking_2015 <- walking_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)
```

@@

```{r}
cycling_2015 <- cycling_2015 |>
  dplyr::select(PUMFID:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2015,
         MODE = "Cycling") |>
  dplyr::rename(ACTCODE = TUI_01)
```

cycling_2015 <- cycling_2015 |> 
  left_join(gss_m_2015, by = 'PUMFID') |>  # Merging the two tables
  filter(LUC_RST %in% c(1,2,3)) |> 
  mutate(Pop_centre =
           case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "non CMA/CA"),
         Province = 
           case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia"))
```

@@

Label the activity ("7" is "Transport to or from activity") and drop the LOCATION because it is already coded as MODE:    
```{r}
cycling_2015 <- cycling_2015 |>
  mutate(act_label = "Transport to or from activity") |>
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)
```

Save data in R format for later use:
```{r}
usethis::use_data(cycling_2015, 
                  overwrite = TRUE)
```

@@

```{r}
rm(gss_e_2015,gss_m_2015)
```

## GSS 2010

@@

```{r}
walking_2010 <- walking_2010 |>
  dplyr::select(RECID, WGHT_EPI,ACTCODE, STARTIME:dest_label) |>
  mutate(YEAR = 2010,
         MODE = "Walking")
walking_2010 <- walking_2010 %>% dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE)
```

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2010 <- gss_m_2010[,c('RECID','LUC_RST','PRV')]

@@

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
walking_2010 <- walking_2010 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
                               ACTCODE == 793 ~ "Travel to/from other socializing (to bars, hospitals, weddings)", # p. 234
                               ACTCODE == 816 ~ "Other outdoor activities/excursions (picnic, car rally, bird watching)", # p. 244
                               ACTCODE == 821 ~ "Walking, hiking, jogging, running", # p. 821
                               ACTCODE == 822 ~ "Bicycling", # p. 244
                               ACTCODE == 831 ~ "Hobbies done mainly for pleasure (painting, sketching, photography)", # p. 244
                               ACTCODE == 871 ~ "Pleasure drives (as the driver)", # p. 245
                               ACTCODE == 872 ~ "Pleasure drives (as a passenger in the car)", # p. 245
                               ACTCODE == 873 ~ "Other pleasure drives (e.g. on a tour bus)", # p. 245
                               ACTCODE == 891 ~ "Travel to/from participation in active sport/outdoor activities", # p. 245
                               ACTCODE == 892 ~ "Travel to/from coaching activities", # p. 245
                               ACTCODE == 893 ~ "Travel to/from hobbies or for the sale of crafts", # p. 245
                               ACTCODE == 894 ~ "Travel to/from other leisure activities", # p. 245
                               ACTCODE == 961 ~ "Reading personal mail (including flyers and advertisements)", # p. 266
                               ACTCODE == 990 ~ "Travel to/from media or communication activities")) |> # p. 266 
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

@@

```{r}
cycling_2010 <- cycling_2010 |>
  dplyr::select(RECID, WGHT_EPI,ACTCODE:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2010,
         MODE = "Cycling")
cycling_2010 <- cycling_2010 %>% dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE)
```

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
gss_m_2010 <- gss_m_2010[,c('RECID','LUC_RST','PRV')]

cycling_2010 <- cycling_2010 |> 
  left_join(gss_m_2010, by = c( 'PUMFID' = 'RECID')) |>  # Merging the two tables
  filter(LUC_RST %in% c(1,2,3)) |> 
  mutate(Pop_centre =
           case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "non CMA/CA"),
         Province = 
           case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia"))
```

@@

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
cycling_2010 <- cycling_2010 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
                               ACTCODE == 793 ~ "Travel to/from other socializing (to bars, hospitals, weddings)", # p. 234
                               ACTCODE == 816 ~ "Other outdoor activities/excursions (picnic, car rally, bird watching)", # p. 244
                               ACTCODE == 821 ~ "Walking, hiking, jogging, running", # p. 821
                               ACTCODE == 822 ~ "Bicycling", # p. 244
                               ACTCODE == 831 ~ "Hobbies done mainly for pleasure (painting, sketching, photography)", # p. 244
                               ACTCODE == 871 ~ "Pleasure drives (as the driver)", # p. 245
                               ACTCODE == 872 ~ "Pleasure drives (as a passenger in the car)", # p. 245
                               ACTCODE == 873 ~ "Other pleasure drives (e.g. on a tour bus)", # p. 245
                               ACTCODE == 891 ~ "Travel to/from participation in active sport/outdoor activities", # p. 245
                               ACTCODE == 892 ~ "Travel to/from coaching activities", # p. 245
                               ACTCODE == 893 ~ "Travel to/from hobbies or for the sale of crafts", # p. 245
                               ACTCODE == 894 ~ "Travel to/from other leisure activities", # p. 245
                               ACTCODE == 961 ~ "Reading personal mail (including flyers and advertisements)", # p. 266
                               ACTCODE == 990 ~ "Travel to/from media or communication activities")) |> # p. 266 
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

Save data in R format for later use:
```{r}
usethis::use_data(cycling_2010, 
                  overwrite = TRUE)
```

```{r}
rm(gss_e_2010,gss_m_2010)
```

## GSS 2005

@@

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
walking_2005 <- walking_2005 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
                               ACTCODE == 793 ~ "Travel to/from other socializing (to bars, hospitals, weddings)", # p. 234
                               ACTCODE == 816 ~ "Other outdoor activities/excursions (picnic, car rally, bird watching)", # p. 244
                               ACTCODE == 821 ~ "Walking, hiking, jogging, running", # p. 821
                               ACTCODE == 822 ~ "Bicycling", # p. 244
                               ACTCODE == 831 ~ "Hobbies done mainly for pleasure (painting, sketching, photography)", # p. 244
                               ACTCODE == 871 ~ "Pleasure drives (as the driver)", # p. 245
                               ACTCODE == 872 ~ "Pleasure drives (as a passenger in the car)", # p. 245
                               ACTCODE == 873 ~ "Other pleasure drives (e.g. on a tour bus)", # p. 245
                               ACTCODE == 891 ~ "Travel to/from participation in active sport/outdoor activities", # p. 245
                               ACTCODE == 892 ~ "Travel to/from coaching activities", # p. 245
                               ACTCODE == 893 ~ "Travel to/from hobbies or for the sale of crafts", # p. 245
                               ACTCODE == 894 ~ "Travel to/from other leisure activities", # p. 245
                               ACTCODE == 961 ~ "Reading personal mail (including flyers and advertisements)", # p. 266
                               ACTCODE == 990 ~ "Travel to/from media or communication activities")) |> # p. 266 
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

Save data in R format for later use:
```{r}
usethis::use_data(walking_2005,
                  overwrite = TRUE)
```

@@

```{r}
cycling_2005 <- cycling_2005 |>
  dplyr::select(RECID, WGHT_EPI, ACTCODE:ENDTIME, DURATION:dest_label) |>
  mutate(YEAR = 2005,
         MODE = "Cycling")
cycling_2005 <- cycling_2005 |> dplyr::rename(
    PUMFID = RECID,
    LOCATION = PLACE) 
```

@@

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
cycling_2005 <- cycling_2005 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
                               ACTCODE == 793 ~ "Travel to/from other socializing (to bars, hospitals, weddings)", # p. 234
                               ACTCODE == 816 ~ "Other outdoor activities/excursions (picnic, car rally, bird watching)", # p. 244
                               ACTCODE == 821 ~ "Walking, hiking, jogging, running", # p. 821
                               ACTCODE == 822 ~ "Bicycling", # p. 244
                               ACTCODE == 831 ~ "Hobbies done mainly for pleasure (painting, sketching, photography)", # p. 244
                               ACTCODE == 871 ~ "Pleasure drives (as the driver)", # p. 245
                               ACTCODE == 872 ~ "Pleasure drives (as a passenger in the car)", # p. 245
                               ACTCODE == 873 ~ "Other pleasure drives (e.g. on a tour bus)", # p. 245
                               ACTCODE == 891 ~ "Travel to/from participation in active sport/outdoor activities", # p. 245
                               ACTCODE == 892 ~ "Travel to/from coaching activities", # p. 245
                               ACTCODE == 893 ~ "Travel to/from hobbies or for the sale of crafts", # p. 245
                               ACTCODE == 894 ~ "Travel to/from other leisure activities", # p. 245
                               ACTCODE == 961 ~ "Reading personal mail (including flyers and advertisements)", # p. 266
                               ACTCODE == 990 ~ "Travel to/from media or communication activities")) |> # p. 266 
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

Save data in R format for later use:
```{r}
usethis::use_data(cycling_2005, 
                  overwrite = TRUE)
```
As we have already processed this year's data, we will clear the Episode and Main files for this year from the computer's memory before uploading any more data

```{r}
rm(gss_e_2005,gss_m_2005)
```

## GSS 1998

@@

The person was at home doing food cleanup (`ACTCODE` = 110), then
went for walking that lasted 30 minutes, came back home and spent 15 minutes relaxing/resting. Here have here another case of a recreational/leisure trip!

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
walking_1998 <- walking_1998 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
                               ACTCODE == 793 ~ "Travel to/from other socializing (to bars, hospitals, weddings)", # p. 234
                               ACTCODE == 816 ~ "Other outdoor activities/excursions (picnic, car rally, bird watching)", # p. 244
                               ACTCODE == 821 ~ "Walking, hiking, jogging, running", # p. 821
                               ACTCODE == 822 ~ "Bicycling", # p. 244
                               ACTCODE == 831 ~ "Hobbies done mainly for pleasure (painting, sketching, photography)", # p. 244
                               ACTCODE == 871 ~ "Pleasure drives (as the driver)", # p. 245
                               ACTCODE == 872 ~ "Pleasure drives (as a passenger in the car)", # p. 245
                               ACTCODE == 873 ~ "Other pleasure drives (e.g. on a tour bus)", # p. 245
                               ACTCODE == 891 ~ "Travel to/from participation in active sport/outdoor activities", # p. 245
                               ACTCODE == 892 ~ "Travel to/from coaching activities", # p. 245
                               ACTCODE == 893 ~ "Travel to/from hobbies or for the sale of crafts", # p. 245
                               ACTCODE == 894 ~ "Travel to/from other leisure activities", # p. 245
                               ACTCODE == 961 ~ "Reading personal mail (including flyers and advertisements)", # p. 266
                               ACTCODE == 990 ~ "Travel to/from media or communication activities")) |> # p. 266 
  dplyr::select(PUMFID, WGHT_EPI, ACTCODE, act_label, STARTIME, ENDTIME, DURATION, origin, destination, orig_label, dest_label, YEAR, MODE, LUC_RST, PRV, Pop_centre, Province)

@@

Label the activity (see the activity codes in the 2010 User's Guide) and drop the LOCATION because it is already coded as MODE:
cycling_1998 <- cycling_1998 |>
  mutate(act_label = case_when(ACTCODE == 2 ~ "Refused information",
                               ACTCODE == 12 ~ "Work for pay at other job(s)", # p. 156
                               ACTCODE == 22 ~ "Looking for work", # p. 156
                               ACTCODE == 23 ~ "Unpaid work in a family business or farm", # p. 156
                               ACTCODE == 30 ~ "Travel during work", # p. 156
                               ACTCODE == 60 ~ "Idle time before/after work", # p. 156
                               ACTCODE == 90 ~ "Travel to/from paid work", # p. 156
                               ACTCODE == 101 ~ "Meal preparation", # p. 164
                               ACTCODE == 110 ~ "Food (or meal) cleanup", # p. 164
                               ACTCODE == 130 ~ "Outdoor cleaning (garbage, snow removal, garage)", # p. 164 
                               ACTCODE == 171 ~ "Gardening/grounds maintenance", # p. 
                               ACTCODE == 172 ~ "Pet care (walking, grooming, feeding)", # p. 164
                               ACTCODE == 190 ~ "Travel to/from unpaid household work", # p. 164
                               ACTCODE == 200 ~ "Baby care/child care (infant to 4 years old)", # p. 174
                               ACTCODE == 210 ~ "Child care", # p. 177 
                               ACTCODE == 240 ~ "Play with children", # p. 177
                               ACTCODE == 291 ~ "Travel to/from personal care activities for household children", # p.177
                               ACTCODE == 292 ~ "Travel to/from personal care activities for household adults",  # p.177
                               ACTCODE == 302 ~ "Everyday shopping: everyday goods and products (clothing, gas, etc.)", # p. 188
                               ACTCODE == 303 ~ "Everyday shopping: Take-out food", # p. 188
                               ACTCODE == 370 ~ "Waiting for purchases or services", # p. 188
                               ACTCODE == 390 ~ "Travel to/from shopping or obtaining services", # p. 188
                               ACTCODE == 491 ~ "Travel to/from restaurant meals", # p. 202
                               ACTCODE == 492 ~ "Travel to/from other personal care activities", # p. 202
                               ACTCODE == 590 ~ "Travel to/from school education activities", # p. 208
                               ACTCODE == 610 ~ "Political, civic activity (e.g. voting, jury duty, city council, donating blood)", # p. 215
                               ACTCODE == 673 ~ "Unpaid babysitting", # p. 215
                               ACTCODE == 674 ~ "Transportation assistance to someone other than a household member", # p. 215
                               ACTCODE == 691 ~ "Travel to/from civic and voluntary activity", # p. 216
                               ACTCODE == 692 ~ "Travel to/from religious services", # p. 216
                               ACTCODE == 791 ~ "Travel to/from attending sports, movies or other entertainment events or visit sites", # p. 234
                               ACTCODE == 792 ~ "Travel to/from socializing at private residences", # p. 234
